Covariance as constraint: Leveraging leaf economic relationships to constrain plant functional type trait estimates

### 2018-01-03 manuscript-md/index.Rmd
Remove Sabina from author list

---
title: "Covariance as constraint: Leveraging leaf economic relationships to constrain plant functional type trait estimates"
author: >
  Alexey N. Shiklomanov$^1$,
  Elizabeth M. Cowdery$^1$,
  Michael Bahn$^2$,
  Sabina Burrascano$^3$,
  Chaeho Byun$^4$,
  Joseph Craine$^5$,
  Andrés Gonzalez-Melo$^6$,
  Alvaro G. Gutiérrez$^7$,
  Steven Jansen$^8$,
  Nathan Kraft$^9$,
  Koen Kramer$^{10}$,
  Vanessa Minden$^{11,12}$
  Ülo Niinemets$^{13}$,
  Yusuke Onoda$^{14}$,
  Enio Egon Sosinski$^{15}$,
  Nadejda A. Soudzilovskaia$^{16}$,
  Michael C. Dietze$^1$
bibliography:
  - library.bib
  - extra.bib
  - tryrefs.bib
csl: new-phytologist.csl
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: no
---
$^1$Department of Earth & Environment, Boston University, Boston, MA 02215, USA;
$^2$Institute of Ecology, University of Innsbruck, 6020 Innsbruck, Austria;
$^3$Department of Environmental Biology, Sapienza University of Rome, Piazzale Aldo Moro 5, 00185, Rome, Italy;
$^4$School of Biological Sciences, Seoul National University, Gwanak-ro 1, 08826, Seoul, Seoul, South Korea;
$^5$Jonah Ventures, Manhattan, KS 66502, USA;
$^6$Universidad del Rosario. Facultad de Ciencias Naturales y Matemáticas. Carrera 26 #63B-48. Bogotá, Colombia;
$^7$Departamento de Ciencias Ambientales y Recursos Naturales, Facultad de Ciencias Agronomicas, Universidad de Chile, Av. Santa Rosa 11315, La Pintana 8820808, Santiago, Chile;
$^8$Institute of Systematic Botany and Ecology, Ulm University, Ulm, Germany;
$^9$Department of Ecology and Evolutionary Biology, University of California Los Angeles, Los Angeles, CA 90095, USA;
$^{10}$Vegetation, Forest, and Landscape Ecology, Wageningen Environmental Research and Wageningen University, Wageningen, Gelderland, The Netherlands;
$^{11}$Institute for Biology and Environmental Sciences, Carl von Ossietzky-University of Oldenburg, Carl von Ossietzky Str. 9-11, 26129 Oldenburg, Germany;
$^{12}$Department of Biology, Ecology and Evolution, Vrije Universiteit Brussel, Pleinlaan 2, 1050 Brussels;
$^{13}$Institute of Agricultural and Environmental Sciences, Estonian University of Life Sciences, Kreutzwaldi 1, 51014 Tartu, Estonia;
$^{14}$Graduate School of Agriculture, Kyoto University, Kyoto, 606-8502, Japan;
$^{15}$Embrapa Temperate Agriculture, Rodovia BR 392, Km 78, CEP 96010-971 Pelotas, RS, Brazil;
$^{16}$Conservation Biology Department, Institute of Environmental Sciences, Leiden University, Leiden, The Netherlands

>>>>

---
title: "Covariance as constraint: Leveraging leaf economic relationships to constrain plant functional type trait estimates"
author: >
  Alexey N. Shiklomanov$^1$,
  Elizabeth M. Cowdery$^1$,
  Michael Bahn$^2$,
  Chaeho Byun$^3$,
  Joseph Craine$^4$,
  Andrés Gonzalez-Melo$^5$,
  Alvaro G. Gutiérrez$^6$,
  Steven Jansen$^7$,
  Nathan Kraft$^8$,
  Koen Kramer$^{9}$,
  Vanessa Minden$^{10,11}$
  Ülo Niinemets$^{12}$,
  Yusuke Onoda$^{13}$,
  Enio Egon Sosinski$^{14}$,
  Nadejda A. Soudzilovskaia$^{15}$,
  Michael C. Dietze$^1$
bibliography:
  - library.bib
  - extra.bib
  - tryrefs.bib
csl: new-phytologist.csl
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: no
    includes:
      in_header: preamble.tex
---
$^1$Department of Earth & Environment, Boston University, Boston, MA 02215, USA;
$^2$Institute of Ecology, University of Innsbruck, 6020 Innsbruck, Austria;
$^3$School of Biological Sciences, Seoul National University, Gwanak-ro 1, 08826, Seoul, Seoul, South Korea;
$^4$Jonah Ventures, Manhattan, KS 66502, USA;
$^5$Universidad del Rosario. Facultad de Ciencias Naturales y Matemáticas. Carrera 26 #63B-48. Bogotá, Colombia;
$^6$Departamento de Ciencias Ambientales y Recursos Naturales, Facultad de Ciencias Agronomicas, Universidad de Chile, Av. Santa Rosa 11315, La Pintana 8820808, Santiago, Chile;
$^7$Institute of Systematic Botany and Ecology, Ulm University, Ulm, Germany;
$^8$Department of Ecology and Evolutionary Biology, University of California Los Angeles, Los Angeles, CA 90095, USA;
$^{9}$Vegetation, Forest, and Landscape Ecology, Wageningen Environmental Research and Wageningen University, Wageningen, Gelderland, The Netherlands;
$^{10}$Institute for Biology and Environmental Sciences, Carl von Ossietzky-University of Oldenburg, Carl von Ossietzky Str. 9-11, 26129 Oldenburg, Germany;
$^{11}$Department of Biology, Ecology and Evolution, Vrije Universiteit Brussel, Pleinlaan 2, 1050 Brussels;
$^{12}$Institute of Agricultural and Environmental Sciences, Estonian University of Life Sciences, Kreutzwaldi 1, 51014 Tartu, Estonia;
$^{13}$Graduate School of Agriculture, Kyoto University, Kyoto, 606-8502, Japan;
$^{14}$Embrapa Temperate Agriculture, Rodovia BR 392, Km 78, CEP 96010-971 Pelotas, RS, Brazil;
$^{15}$Conservation Biology Department, Institute of Environmental Sciences, Leiden University, Leiden, The Netherlands
